Engineering spin squeezing in a 3D optical lattice with interacting spin-orbit-coupled fermions

### 2019-10-04 soc_squeezing/squeezing_paper/main.tex
pushing final version of squeezing paper submitted to PRR

An external laser with Rabi frequency $\Omega$ and wavenumber $k_{\t{L}}$ along the tunneling axis resonantly couples atoms' internal states through the Hamiltonian $\hat H_{\t{laser}}/\hbar = \sum_j \Omega e^{ik_{\t{L}}x_j} \hat c_{j,\up}^\dag \hat c_{j,\dn} + \t{h.c.}$, where $\hat c_{j\alpha}$ is a fermionic annihilation operator for an atom on site $j$ with internal state $\alpha\in\set{\up,\dn}$ and $x_j$ is the position of site $j$.
This laser imprints a position-dependent phase that equates to a momentum kick $k_{\t{L}}$ when an atom changes internal states by absorbing or emitting a photon, thereby generating spin-orbit coupling\cite{wall2016synthetic, livi2016synthetic}.
After absorbing the position dependence of the laser Hamiltonian into fermionic operators through the gauge transformation $\hat c_{j,\up}\to e^{ik_{\t{L}} x_j}\hat c_{j,\up}$, which makes $\hat H_{\t{laser}}$ spatially homogeneous, the atoms are well-described in the tight-binding limit by the Fermi-Hubbard Hamiltonian\cite{esslinger2010fermihubbard}
\begin{align}
  \hat H_{\t{FH}}^{(\phi)}/\hbar
  &= -J \sum_j \p{e^{i\phi} \hat c_{j,\up}^\dag \hat c_{j+1,\up}
  + \hat c_{j,\dn}^\dag \hat c_{j+1,\dn} + \text{h.c.}} \notag \\
  &\qquad + U \sum_j \hat n_{j,\up} \hat n_{j,\dn},
\label{eq:FermiHubbard}
\end{align}
where $J$ is the nearest-neighbor tunneling rate; the SOC angle $\phi\equiv k_{\t{L}}a$ determines the phase gained by spin-up atoms upon tunneling from site $j$ to site $j+1$ (in the gauge-transformed frame) with lattice spacing $a=x_{j+1}-x_j$; $U$ is the on-site interaction energy of two atoms; and $\hat n_{j\alpha}\equiv\hat c_{j\alpha}^\dag \hat c_{j\alpha}$ is a number operator.

The Fermi-Hubbard Hamiltonian can be re-written in the quasi-momentum basis with annihiliation operators $\hat c_{q\alpha}\equiv L^{-1/2}\sum_j e^{-iqx_j}\hat c_{j\alpha}$, where $q$ is a quasi-momentum and $L$ is the total number of lattice sites.
In this basis, the single-particle Hamiltonian exhibits shifted dispersion relations that signify spin-orbit coupling [see Fig.~\ref{fig:protocol_schematic}(b)]:
\begin{align}
  \hat H_{\t{FH,single}}^{(\phi)}/\hbar
  = -2J\sum_q\sp{\cos(qa + \phi) \hat n_{q,\up}
  + \cos(qa) \hat n_{q,\dn}}.
\label{eq:FermiHubbards}
\end{align}
When $U\lesssim J$, interaction energies are too weak for collisions to change the occupancies of single-particle quasi-momentum modes.
Atoms are then pinned to these modes, which form a lattice in quasi-momentum space [see Fig.~\ref{fig:protocol_schematic}(c)]\cite{bromley2018dynamics}.
In this strong-tunneling limit, the Fermi-Hubbard Hamiltonian [Eqn.~\eqref{eq:FermiHubbard}] can be mapped to a spin-$1/2$ system with a collective ferromagnetic Heisenberg interaction and an inhomogeneous axial field, given by\cite{martin2013quantum,rey2014probing, bromley2018dynamics}
\begin{align}
  \hat H_{\t{spin}}/\hbar
  = -\frac{U}{L} \hat{\v S} \c \hat{\v S}
  - \sum_q B_q \hat s_q^\z,
\label{eq:SpinModel}
\end{align}
where $\hat{\v S}=\sum_q\hat{\v s}_q$ is a collective spin operator; $\hat{\v s}_q$ is a spin-1/2 operator for mode $q$ with components $\hat{s}_q^{j=\x,\y,\z}\equiv\frac12\sum_{\alpha,\beta}\hat c_{q\alpha}^\dag\sigma^j_{\alpha\beta}\hat c_{q\beta}$ defined in terms of the Pauli matrices $\sigma^{j=\x,\y,\z}$; the sums over $q$ run over all occupied quasi-momentum modes; and $B_q \equiv -4J\sin(qa+\phi/2)\sin(\phi/2)$ is the SOC-induced axial field.

@@

The entire protocol for preparing a squeezed state via OAT, sketched out in Fig.~\ref{fig:protocol_schematic}(e), reduces to a standard Ramsey protocol with a spin echo: after initially preparing a spin-down (i.e.~$-\uv z$) polarized sample of ultracold atoms populating the lowest Bloch band of a lattice, a fast $\pi/2$ pulse is applied with the clock laser to rotate all spin vectors into $+\uv x$.
The atoms then freely evolve for a variable time $t$ (possibly with spin-echo $\pi$-pulses), after which the amount of metrologically useful spin squeezing, measured by the Ramsey squeezing parameter
\begin{align}
  \xi^2 \equiv
  \min_\theta \braket{\t{var}(\hat S^\perp_\theta)}
  \times N/\abs*{\braket{\hat{\v S}}}^2,
\end{align}
can be determined experimentally from global spin measurements.
Here $\braket{\hat{\v S}}$ is the mean collective spin vector and $\braket{\t{var}(\hat S^\perp_\theta)}$ is the variance of spin measurements along an axis orthogonal to $\braket{\hat{\v S}}$, parameterized by the angle $\theta\in[0,2\pi)$.

@@

The above scheme for OAT achieves optimal spin squeezing that scales as $\xi^2_{\t{opt}}\sim N^{-2/3}$ with minimal intervention, i.e.~a standard Ramsey protocol.
Further improvements upon this scheme can be made by introducing a time-dependent driving field that transforms the OAT Hamiltonian into a two-axis twisting (TAT) one.
While the OAT model initially generates squeezing faster than the TAT model, the squeezing generation rate of OAT (measured in dB per second) falls off with time, while the squeezing generation rate for TAT remains approximately constant until reaching Heisenberg-limited amount of spin squeezing with $\xi^2_{\t{opt}}\sim N^{-1}$\cite{kitagawa1993squeezed, supplementary_material}.

@@

Figure \ref{fig:optima_coherent} shows, for both OAT and TAT protocols, the maximally attainable amount of spin squeezing and the shortest time at which it occurs as a function of the lattice depth $V_0$ and linear lattice size $\ell$ in a single half-filled 2D layer (i.e.~$f=1,N=\ell^2$) of the 3D OLC.
Atoms are confined along the direction transverse to the 2D layer by a lattice of depth 60 $E_{\t{R}}$, where $E_{\t{R}}$ is the atomic lattice recoil energy.
The maximally attainable amount of spin squeezing by each protocol in Fig.~\ref{fig:optima_coherent} depends only on the atom number $N$, while the shortest attainable time is determined by choosing the largest SOC angles $\phi_\x=\phi_\y\equiv\phi$ which saturate $\widetilde{B}/U\approx0.05$.
We impose this constraint on $\widetilde{B}/U$ to ensure validity of the OAT Hamiltonian perturbatively derived in Appendix \ref{sec:derivation_OAT}\cite{supplementary_material}.

\begin{figure*}
\centering
\includegraphics{optima_decoherence.pdf}
\caption{{\bf Optimal squeezing with decoherence} via one- and two-axis twisting in a 2D section of the 3D $^{87}$Sr optical lattice clock (OLC).
In practice, decoherence due to light scattering limits the amount of squeezing that is attainable in the the 3D $^{87}$Sr OLC.
Due to growing squeezing times with increasing system size, the maximal squeezing obtainable via OAT saturates past $\ell\approx30$ sites along each axis of the lattice, with $N\approx10^3$ atoms total.
The more favorable size-dependence of TAT time scales,  however, allow for continued squeezing gains through $\ell=100$ ($N=10^4$).
While the OAT results in ({\bf a}) are exact, the TAT results in ({\bf b}) reflect only a lower bound on the maximum squeezing obtainable, albeit one that is likely close (within a few dB) to the actual value.
Optimal squeezing times in the presence of decoherence are generally smaller than the corresponding times shown in Fig.~\ref{fig:optima_coherent}, as decoherence typically degrades squeezing before it reaches the decoherence-free maximum.
The decoherence considered in this work also limits maximally achievable squeezing to $\sim20$ dB less than the decoherence-free maxima shown in Fig.~\ref{fig:optima_coherent}.
Sample plots of squeezing over time for particular choices of lattice size ($\ell$) and depth ($V_0/E_{\t{R}}$) are provided in the Supplementary Material\cite{supplementary_material}.
}
\label{fig:optima_decoherence}
\end{figure*}

@@

We benchmark the validity of this effective Hamiltonian via exact simulations of the spin [Eqn.~\eqref{eq:SpinModel}] and OAT [Eqn.~\eqref{eq:H_eff}] Hamiltonians in a system of 20 spins, finding that the relative error in maximal squeezing (in dB) of the OAT model is less than 3\% when $\widetilde{B}/U<0.06$\cite{supplementary_material}.

@@

@@

Under the TWA, one accounts for quantum fluctuations during the dynamics by  averaging over different mean field trajectories generated by sampling over different initial conditions chosen to reconstruct the Wigner function of the initial coherent spin state at $t=0$\cite{rey2014probing}.
This method has proven to be successful in simulating quantum spin dynamics.
Using this approach, Fig.~\ref{fig:inelastic_squeezing} shows numerical simulation results of squeezing over time in the presence of inelastic collisions.
For shallow lattices ($V_0\lesssim7E_{\t{R}}$), the effect of inelastic collisions can limit the spin squeezing to $\sim10$ dB.
Thus, in this regime, losses are as relevant as light scattering.
The role of inelastic interactions could be mitigated by either operating at deeper lattices as shown in Fig. \ref{fig:inelastic_squeezing}, or by using nuclear spin states to generate the squeezing instead of the clock states directly.

>>>>

An external laser with Rabi frequency $\Omega$ and wavenumber $k_{\t{L}}$ along the tunneling axis resonantly couples atoms' internal states through the Hamiltonian $\hat H_{\t{laser}}/\hbar = \sum_j \Omega e^{ik_{\t{L}}x_j} \hat c_{j,\up}^\dag \hat c_{j,\dn} + \t{h.c.}$, where $\hat c_{j\alpha}$ is a fermionic annihilation operator for an atom on site $j$ with internal state $\alpha\in\set{\up,\dn}$ and $x_j$ is the position of site $j$.
This laser imprints a position-dependent phase that equates to a momentum kick $k_{\t{L}}$ when an atom changes internal states by absorbing or emitting a photon, thereby generating spin-orbit coupling\cite{wall2016synthetic, livi2016synthetic}.
After absorbing the position dependence of the laser Hamiltonian into fermionic operators through the gauge transformation $\hat c_{j,\up}\to e^{ik_{\t{L}} x_j}\hat c_{j,\up}$, which makes $\hat H_{\t{laser}}$ spatially homogeneous, the atoms are well-described in the tight-binding limit by the Fermi-Hubbard Hamiltonian\cite{esslinger2010fermihubbard}
\begin{align}
  \hat H_{\t{FH}}^{(\phi)}/\hbar
  &= -J \sum_j \p{e^{i\phi} \hat c_{j,\up}^\dag \hat c_{j+1,\up}
  + \hat c_{j,\dn}^\dag \hat c_{j+1,\dn} + \text{h.c.}} \notag \\
  &\qquad + U \sum_j \hat n_{j,\up} \hat n_{j,\dn},
\end{align}
where $J$ is the nearest-neighbor tunneling rate; the SOC angle $\phi\equiv k_{\t{L}}a$ determines the phase gained by spin-up atoms upon tunneling from site $j$ to site $j+1$ (in the gauge-transformed frame) with lattice spacing $a=x_{j+1}-x_j$; $U$ is the on-site interaction energy of two atoms; and $\hat n_{j\alpha}\equiv\hat c_{j\alpha}^\dag \hat c_{j\alpha}$ is a number operator.

The Fermi-Hubbard Hamiltonian can be re-written in the quasi-momentum basis with annihiliation operators $\hat c_{q\alpha}\equiv L^{-1/2}\sum_j e^{-iqx_j}\hat c_{j\alpha}$, where $q$ is a quasi-momentum and $L$ is the total number of lattice sites.
In this basis, the single-particle Hamiltonian exhibits shifted dispersion relations that signify spin-orbit coupling [see Fig.~\ref{fig:protocol_schematic}(b)]:
\begin{align}
  \hat H_{\t{FH,single}}^{(\phi)}/\hbar
  = -2J\sum_q\sp{\cos(qa + \phi) \hat n_{q,\up}
  + \cos(qa) \hat n_{q,\dn}}.
\label{eq:FermiHubbard}
\end{align}
When $U\lesssim J$, interaction energies are too weak for collisions to change the occupancies of single-particle quasi-momentum modes.
Atoms are then pinned to these modes, which form a lattice in quasi-momentum space [see Fig.~\ref{fig:protocol_schematic}(c)]\cite{bromley2018dynamics}.
In this strong-tunneling limit, the Fermi-Hubbard Hamiltonian [Eqn.~\eqref{eq:FermiHubbard}] can be mapped to a spin-$1/2$ system with a collective ferromagnetic Heisenberg interaction and an inhomogeneous axial field, given by\cite{martin2013quantum,rey2014probing, bromley2018dynamics}
\begin{align}
  \hat H_{\t{spin}}/\hbar
  = -\frac{U}{L} \hat{\v S} \c \hat{\v S}
  - \sum_q B_q \hat s_q^\z,
\label{eq:SpinModel}
\end{align}
where $\hat{\v S}=\sum_q\hat{\v s}_q$ is a collective spin operator; $\hat{\v s}_q$ is a spin-1/2 operator for mode $q$ with components $\hat{s}_q^{j=\x,\y,\z}\equiv\frac12\sum_{\alpha,\beta}\hat c_{q\alpha}^\dag\sigma^j_{\alpha\beta}\hat c_{q\beta}$ defined in terms of the Pauli matrices $\sigma^{j=\x,\y,\z}$; the sums over $q$ run over all occupied quasi-momentum modes; and $B_q \equiv -4J\sin(qa+\phi/2)\sin(\phi/2)$ is the SOC-induced axial field.

@@

The entire protocol for preparing a squeezed state via OAT, sketched out in Fig.~\ref{fig:protocol_schematic}(e), reduces to a standard Ramsey protocol with a spin echo: after initially preparing a spin-down (i.e.~$-\uv z$) polarized sample of ultracold atoms populating the lowest Bloch band of a lattice, a fast $\pi/2$ pulse is applied with the clock laser to rotate all spin vectors into $+\uv x$.
The atoms then freely evolve for a variable time $t$ (possibly with spin-echo $\pi$-pulses), after which the amount of metrologically useful spin squeezing, measured by the Ramsey squeezing parameter
\begin{align}
  \xi^2 \equiv
  \min_\theta \braket{\t{var}(\hat S^\perp_\theta)}
  \times N/\abs*{\braket{\hat{\v S}}}^2,
  \label{eq:sqz}
\end{align}
can be determined experimentally from global spin measurements.
Here $\braket{\hat{\v S}}$ is the mean collective spin vector and $\braket{\t{var}(\hat S^\perp_\theta)}$ is the variance of spin measurements along an axis orthogonal to $\braket{\hat{\v S}}$, parameterized by the angle $\theta\in[0,2\pi)$.

@@

The above scheme for OAT achieves optimal spin squeezing that scales as $\xi^2_{\t{opt}}\sim N^{-2/3}$ with minimal intervention, i.e.~a standard Ramsey protocol.
Further improvements upon this scheme can be made by introducing a time-dependent driving field that transforms the OAT Hamiltonian into a two-axis twisting (TAT) one.
While the OAT model initially generates squeezing faster than the TAT model, the squeezing generation rate of OAT (measured in dB per second) falls off with time, while the squeezing generation rate for TAT remains approximately constant until reaching Heisenberg-limited amount of spin squeezing with $\xi^2_{\t{opt}}\sim N^{-1}$ (see Appendix \ref{sec:time_series})\cite{kitagawa1993squeezed}.

@@

Figure \ref{fig:optima_coherent} shows, for both OAT and TAT protocols, the maximally attainable amount of spin squeezing and the shortest time at which it occurs as a function of the lattice depth $V_0$ and linear lattice size $\ell$ in a single half-filled 2D layer (i.e.~$f=1,N=\ell^2$) of the 3D OLC.
Atoms are confined along the direction transverse to the 2D layer by a lattice of depth 60 $E_{\t{R}}$, where $E_{\t{R}}$ is the atomic lattice recoil energy.
The maximally attainable amount of spin squeezing by each protocol in Fig.~\ref{fig:optima_coherent} depends only on the atom number $N$, while the shortest attainable time is determined by choosing the largest SOC angles $\phi_\x=\phi_\y\equiv\phi$ which saturate $\widetilde{B}/U\approx0.05$.
We impose this constraint on $\widetilde{B}/U$ to ensure validity of the OAT Hamiltonian perturbatively derived in Appendix \ref{sec:derivation_OAT} (see also Appendix \ref{sec:benchmarking}).

\begin{figure*}
\centering
\includegraphics{optima_decoherence.pdf}
\caption{{\bf Optimal squeezing with decoherence} via one- and two-axis twisting in a 2D section of the 3D $^{87}$Sr optical lattice clock (OLC).
In practice, decoherence due to light scattering limits the amount of squeezing that is attainable in the the 3D $^{87}$Sr OLC.
Due to growing squeezing times with increasing system size, the maximal squeezing obtainable via OAT saturates past $\ell\approx30$ sites along each axis of the lattice, with $N\approx10^3$ atoms total.
The more favorable size-dependence of TAT time scales,  however, allow for continued squeezing gains through $\ell=100$ ($N=10^4$).
While the OAT results in ({\bf a}) are exact, the TAT results in ({\bf b}) reflect only a lower bound on the maximum squeezing obtainable, albeit one that is likely close (within a few dB) to the actual value.
Optimal squeezing times in the presence of decoherence are generally smaller than the corresponding times shown in Fig.~\ref{fig:optima_coherent}, as decoherence typically degrades squeezing before it reaches the decoherence-free maximum.
The decoherence considered in this work also limits maximally achievable squeezing to $\sim20$ dB less than the decoherence-free maxima shown in Fig.~\ref{fig:optima_coherent}.
Sample plots of squeezing over time for particular choices of lattice size ($\ell$) and depth ($V_0/E_{\t{R}}$) are provided in Appendix \ref{sec:time_series}.
}
\label{fig:optima_decoherence}
\end{figure*}

@@

We benchmark the validity of this effective Hamiltonian via exact simulations of the spin [Eqn.~\eqref{eq:SpinModel}] and OAT [Eqn.~\eqref{eq:H_eff}] Hamiltonians in a system of 20 spins, finding that the relative error in maximal squeezing (in dB) of the OAT model is less than 3\% when $\widetilde{B}/U<0.06$ (see Appendix \ref{sec:benchmarking}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical benchmarking of the OAT model}
\label{sec:benchmarking}
\setcounter{figure}{0}

Here we provide additional information about our benchmarking of the one-axis twisting model against the spin model.
This benchmarking was performed via exact simulations of a 20-spin system.
Fig.~\ref{fig:relative_error} shows the relative error in maximal squeezing of the OAT model (measured against the spin model) as a function of the reduced field variance $\widetilde{B}/U$.
Here squeezing is measured in decibels (dB) by $-10\log_{10}\xi^2$ for the squeezing parameter $\xi^2$ define in Eqn.~\eqref{eq:sqz}.
The relative error in maximal squeezing (in dB) by the OAT model is less than 3\% when $\widetilde{B}/U<0.06$.

\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{relative_error.pdf}
\caption{{\bf Relative error} between maximal squeezing (measured in dB) obtained by the OAT [Eqn.~\eqref{eq:H_eff}] and spin [Eqn.~\eqref{eq:SpinModel}] models of the main text in a system of 20 particles.
The OAT model correctly captures the maximal squeezing (in dB) of the spin model to within 3\% (marked by the horizontal reference line) within the gap-protected regime $\widetilde{B}/U<0.06$.
}
\label{fig:relative_error}
\end{figure}

In principle, spin-changing decoherence compromises the validity of the OAT model, as its perturbative derivation in Appendix \ref{sec:derivation_OAT} relies on spin population remaining primarily within the Dicke manifold.
This assumption breaks down in the presence of, for example, spontaneous emission, which transfers population outside of the Dicke manifold.
Nonetheless, we find decent agreement between the OAT and spin models when decoherence is sufficiently weak (see Fig.~\ref{fig:benchmarking_decay}).

\begin{figure*}
\centering
\includegraphics[width=0.75\textwidth]{benchmarking_decay.pdf}
\caption{{\bf Comparison between the OAT and the spin model in the presence of decoherence.}
({\bf a}) The difference between the maximal squeezing (measured in dB) obtained by the OAT [Eqn.~\eqref{eq:H_eff}] and spin [Eqn.~\eqref{eq:SpinModel}] models increases with the particle number $N$ and the single-particle spontaneous emission rate $\gamma$.
This disagreement is attributed in part to the fact that spontaneous emission transfers population of the collective spin state outside of the Dicke manifold, violating an assumption of the OAT model; see panel ({\bf b}).
The rate of population transfer outside of the Dicke manifold increases with both particle number and spontaneous emission rate.
(Parameters for simulations in this figure: $U=1000$ Hz, $J=200$ Hz, and $\phi=\pi/20$).
}
\label{fig:benchmarking_decay}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Time-series of squeezing via OAT and TAT}
\label{sec:time_series}
\setcounter{figure}{0}

Figure \ref{fig:squeezing_example} shows an example of squeezing over time via OAT and TAT, both with and without decoherence via decay and dephasing of individual spins.
The OAT model initially generates squeezing faster than the TAT model, but the squeezing generation rate of OAT (measured in dB per second) falls off with time.
The squeezing generation rate for TAT, meanwhile, remains approximately constant (in the absence of decoherence) until squeezing via TAT surpasses that of OAT.
In the absence of decoherence, OAT achieves a maximal amount of squeezing that scales as $\xi^2\sim N^{-2/3}$, while TAT achieves Heisenberg-limited squeezing with $\xi^2\sim N^{-1}$.
Note that our method for computing squeezing via TAT in the presence of decoherence (described in Appendix \ref{sec:collective_simulation}) is not capable of computing squeezing for the full range of times shown in Fig.~\ref{fig:squeezing_example}; the corresponding time-series data in this figure is therefore shown up to the point at which this method breaks down.

\begin{figure*}
\centering
\includegraphics{squeezing_example_L40.pdf}
\includegraphics{squeezing_example_L100.pdf}
\caption{{\bf Squeezing via OAT and TAT} in a 2D section of the 3D $^{87}$Sr optical lattice clock, shown for ({\bf a}) $\ell=40$ and ({\bf b}) $\ell=100$ sites per axis (with $N=\ell^2$ atoms total), and a lattice depth of $V_0=4~E_{\t{R}}$, where $E_{\t{R}}$ is the atomic lattice recoil energy.
Atoms are confined along the direction transverse to the 2D layer by a lattice of depth 60 $E_{\t{R}}$.
Squeezing over time is shown for OAT (blue) and TAT (green), both with (solid lines) and without (dashed lines) decoherence via uncorrelated decay and dephasing of individual spins at rates of $0.1~\t{sec}^{-1}$ (see Appendix \ref{sec:decoherence}).
}
\label{fig:squeezing_example}
\end{figure*}

@@

Under the TWA, one accounts for quantum fluctuations during the dynamics by  averaging over different mean field trajectories generated by sampling over different initial conditions chosen to reconstruct the Wigner function of the initial coherent spin state at $t=0$\cite{rey2014probing}.
This method has proven to be successful in simulating quantum spin dynamics.
Using this approach, Fig.~\ref{fig:inelastic_squeezing} shows numerical simulation results of squeezing over time in the presence of inelastic collisions.
For shallow lattices ($V_0\lesssim7E_{\t{R}}$), the effect of inelastic collisions can limit the spin squeezing to $\sim10$ dB.
Thus, in this regime, losses are as relevant as light scattering.
The role of inelastic interactions could be mitigated by either operating at deeper lattices as shown in Fig.~\ref{fig:inelastic_squeezing}, or by using nuclear spin states to generate the squeezing instead of the clock states directly.
